Study of the Empirical Distribution of Ties in Irrational Numbers

### 2020-11-10 Reports/Report - Data Imputation/Code/EmpiricalDistributionTies.Rmd
adding examples of tied sequences

>>>>

### Examples of tied patterns

For illustration, follow we have presented some examples of tied sequences.
How we can observe, the implementation used for Bandt-Pompe symbolization considers the same approach of the time-ordered algorithm.

```{r} 
sqrt2.patterns.D3 = formationPattern(sqrt2.vector, 3, 1, 0)
sqrt2.binary.D3 = binary.equalities(sqrt2.elements.D3)
print('Elements:')
print(sqrt2.elements.D3[which(sqrt2.binary.D3 == 1)[1:10],])
print('Patterns:')
print(sqrt2.patterns.D3[which(sqrt2.binary.D3 == 1)[1:10],])
```
```{r} 
e.patterns.D4 = formationPattern(e.vector, 4, 1, 0)
e.binary.D4 = binary.equalities(e.elements.D4)
print('Elements:')
print(e.elements.D4[which(e.binary.D4 == 1)[1:10],])
print('Patterns:')
print(e.patterns.D4[which(e.binary.D4 == 1)[1:10],])
```
```{r} 
pi.patterns.D6 = formationPattern(pi.vector, 6, 1, 0)
pi.binary.D6 = binary.equalities(pi.elements.D6)
print('Elements:')
print(pi.elements.D6[which(pi.binary.D6 == 1)[1:10],])
print('Patterns:')
print(pi.patterns.D6[which(pi.binary.D6 == 1)[1:10],])
```
